An agent-based model for city networks based on interactions between firms

### 2019-09-26 slides.tex
Update on Overleaf.

\begin{itemize}
    \item Evolutionary Theory of Urban Systems \cite{pumain1997pour} \cite{pumain2006villes}
    \item Adaptive cycles and diffusion on innovation (H{\"a}gerstrand, 1973) 
    \item Path dependence \cite{martinsunley2006information}
    \item Selection and emerging structures of systems
\end{itemize}

@@

  \textit{Central and Eastern European cities within ownership links of firms in 2013.}

@@

@@

Starting from an initial network, at each time step:
\begin{enumerate}
    \item Evolve cities with an interaction model (\cite{raimbault2018indirect} or \cite{cottineau2015growing})
    \item Add a fixed number of links randomly, following a probability function of sizes, sector proximity, and geographical and socio-cultural proximities
\end{enumerate}

>>>>

\begin{itemize}
    \item Evolutionary Theory of Urban Systems \cite{pumain1997pour} \cite{pumain2006villes}
    \item Adaptive cycles and diffusion on innovation \cite{Hagerstrand1968Innovation}
    \item Path dependence \cite{martin2006path}
    \item Selection and emerging structures of systems
\end{itemize}

@@

  \textit{Central and Eastern European cities within ownership links of firms in 2013}

@@

\item Cities are defined by their profile regarding the proportion of firms in the different sectors. Links between cities are created in an iterative way, taking into account:
    \begin{itemize}
        \item geographical proximity (distance or effective accessibility)
        \item geopolitical proximity (belonging to the same country or single market $\rightarrow$ application to Brexit)
        \item city size (economic size as GDP) 
        \item economic similarity (e.g. cosine distance between sector proximity as done in \cite{2019arXiv190505106C}
        \item previous linkages 
    \end{itemize}

% j'ai mis ca plus pour moi,enfin pour moi c'est plus clair pour la presentation

@@

Starting from an initial network, at each time step:
\begin{enumerate}
    \item Evolve cities with an interaction model (\cite{raimbault2018indirect} or \cite{cottineau2015growing})
    \item Add a fixed number of links randomly, following a probability function of sizes, sector proximity, and geographical and socio-cultural proximity
\end{enumerate}
